Flowchart of Current Algorithm

### 2008-10-26 docs/flowchart/flowchart.tex
small updates
some more comments + spell check

Here we outline the algorithm currently implemented in the code.  Our
starting point for this description are the series of papers describing
the development of the algorithm:
\begin{itemize}
\item {\em Low Mach Number Modeling of Type Ia
  Supernovae. I. Hydrodynamics,} A.~S.~Almgren, J.~B.~Bell, 
  C.~A.~Rendleman, \& M.~Zingale 2006, ApJ, 637, 922 (henceforth
  paper~I)
\item {\em Low Mach Number Modeling of Type Ia Supernovae. II. Energy
  Evolution,} A.~S.~Almgren, J.~B.~Bell, C.~A.~Rendleman, \& M.~Zingale
  2006, ApJ, 649, 927 (henceforth paper~II)
\item {\em Low Mach Number Modeling of Type Ia Supernovae. III. Reactions,}
A.~S.~Almgren, J.~B.~Bell, A.~Nonaka, \& M.~Zingale
  2008, ApJ, 684, 449 (henceforth paper~III)
\item {\em Low Mach Number Modeling of Type Ia Supernovae. IV. White Dwarf Convection,}
A.~S.~Almgren, J.~B.~Bell, A.~Nonaka, \& M.~Zingale,
  in perparation (henceforth paper~IV)
\end{itemize}
We also carry over some ideas from our small-scale low Mach number algorithm
for astrophysical flows:
\begin{itemize}
\item {\em Adaptive Low Mach Number Simulations of Nuclear Flames,}
J.~B.~Bell, M.~S.~Day, C.~A.~Rendleman, S.~E.~Woosley, \& M.~Zingale
2004, JCP, 195, 2, 677 (henceforth BDRWZ)
\end{itemize}

@@

\item We add thermal diffusion.
\end{itemize}
%
The advance of the state through a single timestep appears as:

@@

\item
Define
\begin{eqnarray}
\gammabar^{(1)}        &=& {\rm{\bf Avg}} \left[ \Gamma_1(\rho^{(1)}, p_0^{n}, X_k^{(1)}) \right] \enskip , \\
 {\beta   }_0^{(1)}    &=& \beta   \left(\rho_0^{n}, p_0^{n}, \gammabar^{(1)}\right) \enskip .
\end{eqnarray}

@@

  \item Compute the species edge states, $(\rho X_k)^{(1),\nph,\star}$,
  for the conservative update of $(\rho X_k)$. 
  Here we predict $\rho'$ and $X_k$ to the edges to obtain 
  $\rho^{'(1),\nph,\star}$ and $X_k^{(1),\nph,\star}$ using a second-order
  Taylor expansion in space and time, as described in paper II,
  Appendix A, using $\Vb = \uadvone+w_0^{\nph,\star} \er$.  We use the base
  state density, $\rho_0$, to convert this to an edge state for $\rho$,

\begin{equation}
\rho^{(1),\nph,\star} = 
\rho^{'(1),\nph,\star} + \frac{\rho_0^n + \rho_0^{(2),\star}}{2} \enskip ,
\end{equation}

@@

\item[spherical:] See {\tt MAESTO/docs/eta\_notes} for working notes until we finlize 
the details.

@@

   We note that for spherical geometry, the edge state of $(\rho h)_0$
   is computed by averging $h_0 \equiv (\rho h)_0/\rho_0$ and $\rho_0$
   to the edge separately, and then computing 
   ${(\rho h)_0}_{r+1/2} = {\rho_0}_{r+1/2} {h_0}_{r+1/2}$.

@@

   \item Evolve $(\rho h)^{(1)} \rightarrow (\rho h)^{(2)}$ without
     explicitly including the reaction terms,

>>>>

Here we outline the algorithm currently implemented in the code.  Our
starting point for this description are the series of papers describing
the development of the algorithm:
\begin{itemize}
\item {\em Low Mach Number Modeling of Type Ia
  Supernovae. I. Hydrodynamics,} A.~S.~Almgren, J.~B.~Bell, 
  C.~A.~Rendleman, \& M.~Zingale 2006, ApJ, 637, 922 (henceforth
  paper~I)
\item {\em Low Mach Number Modeling of Type Ia Supernovae. II. Energy
  Evolution,} A.~S.~Almgren, J.~B.~Bell, C.~A.~Rendleman, \& M.~Zingale
  2006, ApJ, 649, 927 (henceforth paper~II)
\item {\em Low Mach Number Modeling of Type Ia Supernovae. III. Reactions,}
A.~S.~Almgren, J.~B.~Bell, A.~Nonaka, \& M.~Zingale
  2008, ApJ, 684, 449 (henceforth paper~III)
\item {\em Low Mach Number Modeling of Type Ia Supernovae. IV. White Dwarf Convection,}
A.~S.~Almgren, J.~B.~Bell, A.~Nonaka, \& M.~Zingale,
  in preparation (henceforth paper~IV)
\end{itemize}
We also carry over some ideas from our small-scale low Mach number algorithm
for astrophysical flows:
\begin{itemize}
\item {\em Adaptive Low Mach Number Simulations of Nuclear Flames,}
J.~B.~Bell, M.~S.~Day, C.~A.~Rendleman, S.~E.~Woosley, \& M.~Zingale
2004, JCP, 195, 2, 677 (henceforth BDRWZ)
\end{itemize}

@@

\item We add thermal diffusion.

\item We added the volume-discrepancy term to the velocity constraint
equation.
\end{itemize}
%
The advance of the state through a single timestep appears as:

@@

\item
Define
\begin{eqnarray}
\gammabar^{(1)}        &=& {\rm{\bf Avg}} \left[ \Gamma_1(\rho^{(1)}, p_0^{n}, X_k^{(1)}) \right] \enskip , \\
 {\beta   }_0^{(1)}    &=& \beta   \left(\rho_0^{n}, p_0^{n}, \gammabar^{(1)}\right) \enskip .
\end{eqnarray}
Here $\beta_0$ is computed as described in paper~III, Appendix C.

@@

  \item Compute the species edge states, $(\rho X_k)^{(1),\nph,\star}$,
  for the conservative update of $(\rho X_k)$. 
  Here we predict $\rho'$ and $X_k$ to the edges to obtain 
  $\rho^{'(1),\nph,\star}$ and $X_k^{(1),\nph,\star}$ using a second-order
  Taylor expansion in space and time, as described in paper II,
  Appendix A, using $\Vb = \uadvone+w_0^{\nph,\star} \er$.  We use the base
  state density, $\rho_0$, to convert this to an edge state for $\rho$,
  \MarginPar{why don't we do something higher order here for plane-parallel?}
\begin{equation}
\rho^{(1),\nph,\star} = 
\rho^{'(1),\nph,\star} + \frac{\rho_0^n + \rho_0^{(2),\star}}{2} \enskip ,
\end{equation}

@@

\item[spherical:] See {\tt MAESTRO/docs/eta\_notes} for working notes until we finalize 
the details.

@@

   We note that for spherical geometry, the edge state of $(\rho h)_0$
   is computed by averaging $h_0 \equiv (\rho h)_0/\rho_0$ and $\rho_0$
   to the edge separately, and then computing 
   ${(\rho h)_0}_{r+1/2} = {\rho_0}_{r+1/2} {h_0}_{r+1/2}$.

@@

   We note that for spherical geometry, the edge state of $(\rho h)_0$
   is computed by averaging $h_0 \equiv (\rho h)_0/\rho_0$ and $\rho_0$
   to the edge separately, and then computing 
   ${(\rho h)_0}_{r+1/2} = {\rho_0}_{r+1/2} {h_0}_{r+1/2}$.
   \item Evolve $(\rho h)^{(1)} \rightarrow (\rho h)^{(2)}$ without
     explicitly including the reaction terms,
